---
title: "SU.CRDB.CS5200"
author: Yuchao Su
date: Oct 2, 2021
output:
  pdf_document: default
  html_notebook: default
---
## Basic Config
```{r}
library(RSQLite)
fpath = ("C:/Users/suyuc/Desktop/CS5200/")
dbfile = "Course_Info.db"

dbcon <- dbConnect(RSQLite::SQLite(), paste0(fpath,dbfile))
```
## Enable foreign key
```{sql connection=dbcon}
PRAGMA foreign_keys = ON;
```

```{sql connection=dbcon}
DROP TABLE  IF EXISTS Unit;
```
```{sql connection=dbcon}
DROP TABLE  IF EXISTS Course;
```
```{sql connection=dbcon}
DROP TABLE  IF EXISTS Prerequisite;
```
```{sql connection=dbcon}
DROP TABLE  IF EXISTS Lesson;
```
```{sql connection=dbcon}
DROP TABLE  IF EXISTS Subject;
```

## Create Table
```{sql connection=dbcon}
CREATE TABLE Course(
cid TEXT PRIMARY KEY NOT NULL,
title TEXT NOT NULL,
lengthInDays INT NOT NULL
);
```

```{sql connection=dbcon}
CREATE TABLE Unit(
cid TEXT NOT NULL,
tid INT NOT NULL,
PRIMARY KEY(cid,tid),
FOREIGN KEY(cid) REFERENCES Course(cid),
FOREIGN KEY(tid) REFERENCES Lesson(tid)
);
```

```{sql connection=dbcon}
CREATE TABLE Lesson(
tid INT PRIMARY KEY NOT NULL,
title TEXT NOT NULL,
lengthInHrs INT NOT NULL,
subjectId INT NOT NULL,
FOREIGN KEY(subjectId) REFERENCES Subject(subjectId)
);
```

```{sql connection=dbcon}
CREATE TABLE Subject(
subjectId INT PRIMARY KEY,
content TEXT,
CHECK (content IN ("ML", "SQL", "R", "JAVA"))
);
```


```{sql connection=dbcon}
CREATE TABLE Prerequisite(
tid INT NOT NULL,
pid INT NOT NULL,
PRIMARY KEY(tid,pid),
FOREIGN KEY(pid) REFERENCES Lesson(tid),
FOREIGN KEY(pid) REFERENCES Lesson(tid)
);
```

## Test Table
```{sql connection=dbcon}
INSERT INTO Course(cid,title,lengthInDays) VALUES
("CS5200","DB",2),
("EECE5550","MR",3),
("EECE2560","C++",5);
```

```{sql connection=dbcon}
INSERT INTO Subject(subjectId,content) VALUES
(1,"R"),
(2,"ML"),
(3,"JAVA"),
(4,"SQL");
```

```{sql connection=dbcon}
INSERT INTO Lesson(tid,title,lengthInHrs,subjectID) VALUES
(1,"Intro_R",4,1),
(2,"Intro_C++",4,2),
(3,"Intro_JAVA",4,3),
(4,"Intro_SQL",4,4);
```

```{sql connection=dbcon}
INSERT INTO Unit(cid,tid) VALUES
("CS5200",1),
("EECE2560",2);
```

```{sql connection=dbcon}
INSERT INTO Prerequisite(tid,pid) VALUES
(1,4),
(2,3);
```

```{sql connection=dbcon}
SELECT * FROM Unit
```

```{sql connection=dbcon}
SELECT * FROM Lesson
```

```{sql connection=dbcon}
SELECT * FROM Prerequisite
```

```{sql connection=dbcon}
SELECT * FROM Subject
```

```{sql connection=dbcon}
SELECT * FROM Course
```


```{r}
dbDisconnect(dbcon)
```

## How to update table constraints to integrate extensible dataset?
For SQLITE, you can not simply do a “ALTER TABLE” command to update table constraints. I am sharing
an easy solution according to the SQLITE Documentation which allows you to update your table constraints
instead of excuting drop the table, update the schema, recreate the table and then insert new records.

- Give wirte access: dbExecute(dbcon, “PRAGMA writable_schema = 1”)
- Overwrite schema with your new constraints,e.g.
  ```
    UPDATE sqlite_master SET sql =
    "CREATE TABLE Subject(
     subjectId INT NOT NULL,
     content TEXT NOT NULL,
     PRIMARY KEY (sid),
     CHECK (content IN (’ML’, ’SQL’, ’R’, ’JAVA’,’C’, ’C++’))"
     WHERE type = ’table’ AND name = ’Subject’;
  ```
- Reopen/load SQLITE, simply restart SQLITE CLI.
- Update table with new constraints happliy, you can always check your updated schema by use “.schema {TABLE_NAME}” command before you insert tuples.