
```{r}
library(RSQLite)
library(XML)
library(DBI)
library(knitr)

xmlfile <- "Books-v3.xml"
xmlDOM <- xmlParse(xmlfile)
dbfile = "Book.db"
dbcon <- dbConnect(RSQLite::SQLite(), dbfile)
r <- xmlRoot(xmlDOM)
numBook <- xmlSize(r)
```


##Q2 Create a SQLite database that implements the schema
```{sql connection=dbcon}
DROP TABLE IF EXISTS book
```

##Create Table
```{sql connection=dbcon}
CREATE TABLE book(
id INT PRIMARY KEY,
author TEXT,
title TEXT,
edition INT,
genre TEXT,
price TEXT,
publish_date DATE,
description TEXT
)
```

##Q3Load the XML data from the file into R data frames
##Create DataFrame
```{r}
book.df <- data.frame(id = vector(mode = "integer", length = numBook),
                      author = vector(mode = "character", length = numBook),
                      title = vector(mode = "character", length = numBook),
                      edition = vector(mode = "integer", length = numBook),
                      genre = vector(mode = "character", length = numBook),
                      price = vector(mode = "character", length = numBook),
                      publish_date = vector(mode = "character", length = numBook),
                      description = vector(mode = "character", length = numBook))

```



##Parsing XML Into DataFrame
```{r}
for(i in 1:numBook)
{
  abook <- r[[i]]
  
  id <- xmlAttrs(abook)
  author <- xmlValue(abook[[1]])
  title <- xmlValue(abook[[2]])
  if(xmlName(abook[[3]]) == "edition")
  {
    edition <- xmlValue(abook[[3]])
    genre <- xmlValue(abook[[4]])
    price <- xmlValue(abook[[5]])
    publish_date <- xmlValue(abook[[6]])
    description <- xmlValue(abook[[7]])
  }
  else
  {
    edition <- NULL
    genre <- xmlValue(abook[[3]])
    price <- xmlValue(abook[[4]])
    publish_date <- xmlValue(abook[[5]])
    description <- xmlValue(abook[[6]])}
  
  book.df[i,]$id <- id
  book.df[i,]$author <- author
  book.df[i,]$edition <- edition
  book.df[i,]$title <- title
  book.df[i,]$genre <- genre
  book.df[i,]$price <- price
  book.df[i,]$publish_date <- publish_date
  book.df[i,]$description <- description
}

```

##Q4 Transform data types as necessary and then save the data frames to the appropriate tables in the database using a strategy of your choice
```{r}
dbWriteTable(dbcon,"book",book.df,overwrite=T)
```

```{sql connection=dbcon}
SELECT * FROM book
```
##Q5 A What is the number of genres have at least three books?
```{sql connection=dbcon}
SELECT COUNT(*) FROM (SELECT genre,COUNT(*) FROM book GROUP BY genre HAVING COUNT(id) >= 3)
```
##Q5 B What is the most recent year in which a publication was published?
```{sql connection=dbcon}
SELECT MAX(strftime('%Y', publish_date)) as Recent_Year FROM book
```
##Q5 C Find the number of books and average price for each genre.
```{sql connection=dbcon}
SELECT genre, COUNT(*), AVG(price) FROM book GROUP BY genre
```
##Q5 D List the title and author of all books that are less than 0.8*AVG or more than 1.2*AVG, where AVG is the average price of all books. 
```{sql connection=dbcon}
SELECT title, author FROM book WHERE (price < (SELECT AVG(price)*0.8 FROM book)) or (price > (SELECT AVG(price)*1.2 FROM book))
```


```{r}
dbDisconnect(dbcon)
```


